### 2014-06-27 1_introduction/introduction.tex
auto

In summary, the first main objective is to derive a scalar and representative statistical model for POLSAR data.
%The theoretical foundation is the commonly agreed Circular Complex Normal distributions proposed in \cite{Goodman_JOptSocAm_76}. %***IVM you need a reference here!!
%Theory development is based on applying the statistical variable change theorem on the proposed scalar observable.
%The theoretical model is validated by matching the functional PDF or the simulated histogram with real-life captured data.
The second main objective is to derive homoskedastic measures of distance despite its multiplicative and heteroskedastic nature.
This is first applied on the simpler case of SAR data. %devided into a few smaller objectives.
%For this purpose, first log transformation is shown to not only convert the multiplicative noise model into an adaptive one, 
%  it also results in a homoskedastic statistical model.
%From this consistent sense of variance, the second step illustrates the consistent sense of contrast and distance.
%After these models are validated against practical data, their beneficial applications are further explored.
To combine these two seemingly disconnected threads of research, the results for SAR are extended to POLSAR,
  since the thesis also shows that the POLSAR models are a generic multi-dimensional superset of the traditional SAR data. %***IVM I changed "version" to "superset" in the sentence above. Please check if you are comfortable with that change, and if not, change it back!
%Thus the homoskedastic theoretical models and their benefits are extended from SAR to POLSAR.   
%The 3 paragraphs are collapsed into 1: to address Prof Vun's comment:
%(comment: you are stating the objectives repetitively so far – I counted three time so far, and confuse the results obtained with the objectives. There is no need to re-emphasize the objective if the write-up is clear)

>>>>

In summary, the first main objective is to derive a scalar and representative statistical model for POLSAR data.
%The theoretical foundation is the commonly agreed Circular Complex Normal distributions proposed in \cite{Goodman_JOptSocAm_76}. %***IVM you need a reference here!!
%Theory development is based on applying the statistical variable change theorem on the proposed scalar observable.
%The theoretical model is validated by matching the functional PDF or the simulated histogram with real-life captured data.
The second main objective is to derive homoskedastic measures of distance despite its multiplicative and heteroskedastic nature.
The proposed generic models are applicable to multi-dimensional POLSAR data.
Moreover, when the multi-dimensional data is collapsed into one dimension, the specific case of the proposed model matches perfectly with the model proposed by Arsenault \cite{Arsenault_JOptSocAm_1976}.
Thus - even before performing detailed evaluation - there is good evidence that the proposed generic models are at least as appropriate as the widely accepted model cited above.
%This is first applied on the simpler case of SAR data. %devided into a few smaller objectives.
%%For this purpose, first log transformation is shown to not only convert the multiplicative noise model into an adaptive one, 
%%  it also results in a homoskedastic statistical model.
%%From this consistent sense of variance, the second step illustrates the consistent sense of contrast and distance.
%%After these models are validated against practical data, their beneficial applications are further explored.
T%o combine these two seemingly disconnected threads of research, the results for SAR are extended to POLSAR,
%  since the thesis also shows that the POLSAR models are a generic multi-dimensional superset of the traditional SAR data. %***IVM I changed "ver%sion" to "superset" in the sentence above. Please check if you are comfortable with that change, and if not, change it back!
%%Thus the homoskedastic theoretical models and their benefits are extended from SAR to POLSAR.   
%%The 3 paragraphs are collapsed into 1: to address Prof Vun's comment:
%%(comment: you are stating the objectives repetitively so far – I counted three time so far, and confuse the results obtained with the objectives. There is no need to re-emphasize the objective if the write-up is clear)

### 2014-06-27 3/sar.tex
auto

Let us now consider the population expected mean and variance of the four statistical distributions for these observables, i.e. $A, A_1, I, I_1$.
They are given in Table \ref{tbl:orginal_sar_avg_var}. 
If spatial homogeneity is defined as an imaging area having the same back-scattering coefficient $\sigma$,
  then over a homogeneous scene, the measured values can then be considered as samples coming from a single stochastic process.
However, over heterogeneous areas where $\sigma$ varies significantly,
  it is then evidently clear that: the amplitude  as well as the intensity of SAR data suffer from hetoroskedastic phenomena. 
%  which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of mean.
This means that  the conditional expected variance of SAR data is dependent on the conditional expectation of the mean.   
In the context of speckle filtering which aims to estimate the unknown parameter $\sigma$,
  Table \ref{tbl:orginal_sar_avg_var} also clearly indicates an ambiguous circle:
in the original domain, estimating variance is equal to estimating the mean, but this is as hard to estimation as the variance.

@@

The consistent feature is explored and illustrated in this section from two different perspectives. 
First, the back-scattering coefficient $\sigma$ is assumed to be \textit{known a priori}.
With that, let us consider the dispersion random 
variable which is defined as the distance between an observable sample and its expected value:

@@

>>>>

Let us now consider the population expected mean and variance of the four statistical distributions for these observables, i.e. $A, A_1, I, I_1$.
They are given in Table \ref{tbl:orginal_sar_avg_var}. 
If spatial homogeneity is defined as an imaging area having the same back-scattering coefficient $\sigma$,
  then over a homogeneous scene, the measured values can then be considered as samples coming from a single stochastic process.
However, over heterogeneous areas where $\sigma$ varies significantly,
  it is then evidently clear that: the amplitude  as well as the intensity of SAR data suffer from hetoroskedastic phenomena. 
%  which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of mean.
%This means that  the conditional expected variance of SAR data is dependent on the conditional expectation of the mean.
In statistical context, heteroskedasticity and homoskedasticity are terms defined to denote the fact that different sub-populations of a given set of samples can have different or similar variability respectively.
In the context of SAR (and POLSAR) imagery, they respectively denote the fact that different areas in a given image can have different different or similar sample variance, depending on the underlying signal $\sigma$.
In the context of speckle filtering which aims to estimate the unknown parameter $\sigma$,
  Table \ref{tbl:orginal_sar_avg_var} also clearly indicates an ambiguous circle:
in the original domain, estimating variance is equal to estimating the mean, but this is as hard to estimation as the variance.

@@

The consistent feature is explored and illustrated in this section from two different perspectives.

\subsection{The Distance and Log-Distance Models}

First, the back-scattering coefficient $\sigma$ is assumed to be \textit{known a priori}.
With that, let us consider the dispersion random 
variable which is defined as the distance between an observable sample and its expected value:

@@

\subsection{The Dispersion and Contrast Models}

### 2014-06-27 6/conclusional_discussion.tex
auto

The
                proposed scalar models for POLSAR also have limitations.
It
                calls for a dimensional reduction operation, which is
                probably not lossless.
Thus
                while the determinant of POLSAR covariance matrix is
                said to be "highly representative", it is definitely not
                fully representative of the data.
Intuitively,
                this is similar to the use of magnitude as being
                representative of a complex number, which also is not
                fully representative of the two-dimensional number.
But it is important to emphasize that,
                just like the magnitude is invariant to the rotation of
                the reference frame, the POLSAR determinant is also
                invariant to polarization basis transformation.

@@

Although
                the proposed models may have certain limitations, its
                potentials still mostly stays undiscovered.
Since
                the assumptions of partial and full monostatic POLSAR
                models are quite minimal, they are probably also
                applicable to other types of SAR-based data such as: Interferrometric SAR (InSAR), Polarimetric Interferrometric SAR (POLINSAR) 
                or bistatic POLSAR data.
In addition, further experiments can be done to determine whether some existing SAR data processing techniques for SAR can be equally applicable to POLSAR data.
%                Also,
%                it may be interesting time to choose some existing data
%                processing techniques for SAR and showing them
%                applicable to POLSAR data.

>>>>

Since the full POLSAR data is multi-dimensional and the proposed models are scalar,
  by their own definition, they are not perfect.
They inherently suffer from a loss of dimension.  
%The
%                proposed scalar models for POLSAR also have limitations.
%It
%                calls for a dimensional reduction operation, which is
%                probably not lossless.
Thus
                while the determinant of POLSAR covariance matrix is
                said to be "highly representative", it is definitely not
                fully representative of the data.
This restricts the use of the models to a class of porblem where a single scalar decision, ranking, sorting or classification answer is required from the complex dataset.
They however, are hopefully the most practical way to answer some common types of commonly asked questions such as:
  ``what is the best speckle filter for the given data set?'' or
  ``what type of surface does a region of interest belong to?''.
On the other hand, the proposed models might not be very useful in applications,
  where the relationship among each dimensional component is used to make further inferences.

Intuitively,
                their use is similar to the use of magnitude as being
                representative of a complex number, which also is not
                fully representative of the two-dimensional number.
But it is important to emphasize that,
                just like the magnitude is invariant to the rotation of
                the reference frame, the POLSAR determinant is also
                invariant to polarization basis transformation.

@@

%Although
%                the proposed models may have certain limitations, its
%                potentials still mostly stays undiscovered.
Building up from the proposed models, several possible future work has been identified.
Since
                the assumptions of partial and full monostatic POLSAR
                models are quite minimal, they are probably also
                applicable to other types of SAR-based data such as: Interferrometric SAR (InSAR), Polarimetric Interferrometric SAR (POLINSAR) 
                or bistatic POLSAR data.
In addition, further experiments can be done to determine whether some existing SAR data processing techniques for SAR can be equally applicable to POLSAR data.
%                Also,
%                it may be interesting time to choose some existing data
%                processing techniques for SAR and showing them
%                applicable to POLSAR data.
